Abstractions for Type-Level Programming

### 2022-04-21 preprint.tex
Do TODO

% TODO: Add a sentence about the state of adoptions of these ideas

@@

@@

% TODO: Add an example

>>>>

@@

A prototype of our Scala extension is available online, in a branch of the dotty-staging repository\footnote{\texttt{git clone git@github.com:dotty-staging/dotty.git --branch add-transparent-7}}.
Although the ideas presented in this did not reach the production stage, our prototype influenced the design of match types (\Cref{chap:match-types}) which are now part of the Scala 3 language.

@@

### 2022-04-21 thesis.tex
Add Richard's comments
Define Λ and V
Do TODOs
Do TODO

In Scala~3, the rules for implicit ambiguities changed to take implicit parameters into account, thus introducing another, more direct, disambiguation mechanism.
All else being equal, an implicit definition that takes some implicit parameters is considered to be less specific than an implicit definition that takes none~\citep[Changes in Implicit Resolution]{odersky2013scala}.
As a result, implicit-based type-level programs written in Scala~3 do not need to use the patterns of ambiguities and priorities presented in this section (\ref{subsec:implicit-priorities} and \ref{subsec:implicit-ambiguities}).
TODO

@@

This chapter is inspired by Andrea Veneziano's semester project entitled "Strongly-typed regular expressions in Dotty".
In his project, Andrea implemented a regex library in two different flavors, one based on match types and the other based on generalized singleton types, with the objective to compare the two approaches in terms of expressivity and ease of use.
The present chapter is a reboot of the match-type side of that project.
We plan to submit this work to the upcoming Scala Symposium.

@@

We obtained the measurements presented in this chapter by averaging independent compilations on warm compilers, which we executed on an i7-7700K processor running Oracle JVM~1.8.0\_212 and Linux.
For the implicit and match type benchmarks, we used the latest version of Scala at the time of writing (3.1.2).
For the generalized singleton benchmarks, we used our prototype, which lives in a branch of the dotty-staging repository\footnote{\texttt{git clone git@github.com:dotty-staging/dotty.git --branch add-transparent-7}}.

>>>>

In Scala~3, the rules for implicit ambiguities changed to take implicit parameters into account, thus introducing another, more direct, disambiguation mechanism.
All else being equal, an implicit definition that takes some implicit parameters is considered to be less specific than an implicit definition that takes none~\citep[Changes in Implicit Resolution]{odersky2013scala}.
As a result, implicit-based type-level programs written in Scala~3 do not need to use the patterns of ambiguities and priorities presented in this section (\ref{subsec:implicit-priorities} and \ref{subsec:implicit-ambiguities}).

@@

This chapter is inspired by Andrea Veneziano's semester project entitled "Strongly-typed regular expressions in Dotty".
In his project, Andrea implemented a regex library in two different flavors, one based on match types and the other based on generalized singleton types, with the objective to compare the two approaches in terms of expressivity and ease of use.
The present chapter is a reboot of the match-type side of that project.
This work is under submission at the Scala Symposium (2022).

@@

We obtained the measurements presented in this chapter by averaging independent compilations on warm compilers, which we executed on an i7-7700K processor running Oracle JVM~1.8.0\_212 and Linux.
For the implicit and match type benchmarks, we used the latest version of Scala at the time of writing (3.1.2).
For the generalized singleton benchmarks, we used our prototype, which is available in a branch of the dotty-staging repository\footnote{\texttt{git clone git@github.com:dotty-staging/dotty.git --branch add-transparent-7}}.
